Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-24 analysis/paper/paper.Rmd
moved Impacts to Adult Returns to Discussion

A few things that need to be clarified in this section:
* Why were the dates Sept 1 - Nov 17 chosen? They make sense, but we should include our rationale
* Where did the temperature data come from? Hobo? Stream gauge? The methods say temperature data from 2019 was used, but the results seem to use 2020? 
* Why does it look like we only ran it for dates in 2020? Is that the only year we had temperature data for? Would the results look different if we used temperature data from a different year?
* The lengths of pikeminnow: did we only use pikeminnow we caught in the fall to get average length? Is there a difference in lengths between 2019 and 2020? 
* There needs to be more explanation of the inverts vs. fish. What proportion went to each and why? Did it change through time? Based on literature at all? 
* Where is the data that was used to get a weight of 12 g for Chinook emigrant? Was that for Chinook presmolts, or a combination of smolts and presmolts? If the latter, can we filter it to look at the average weight for presmolts only? And maybe smolts only for a different analysis? 
* Could we run a similar model for the spring emigration period? Figure out the dates, look at lengths of pikeminnow from the spring, convert to average weight, use average size of Chinook smolts (not presmolts) from all the Upper Salmon traps? Kevin can work on converting the spring catch into some kind of estimate of pikeminnow at Deadwater in the spring

@@

<!-- After making some assumptions (e.g., on SARs) attempt to estimate how results from objective #3 could translate into impacts on adult returns (via a thought experiment or simulation approach) -->

<!-- Currently only using one bioenergetics model run. Could incorporate more bioenergetics models, but if so then maybe consider focusing on a single abundance estimator (e.g. Schnabel) to avoid too many combinations in the results -->

@@

<!-- Need to add Nick's figures here -->

@@

>>>>

<!--
A few things that need to be clarified in this section:
* Why were the dates Sept 1 - Nov 17 chosen? They make sense, but we should include our rationale
* Where did the temperature data come from? Hobo? Stream gauge? The methods say temperature data from 2019 was used, but the results seem to use 2020? 
* Why does it look like we only ran it for dates in 2020? Is that the only year we had temperature data for? Would the results look different if we used temperature data from a different year?
* The lengths of pikeminnow: did we only use pikeminnow we caught in the fall to get average length? Is there a difference in lengths between 2019 and 2020? 
* There needs to be more explanation of the inverts vs. fish. What proportion went to each and why? Did it change through time? Based on literature at all? 
* Where is the data that was used to get a weight of 12 g for Chinook emigrant? Was that for Chinook presmolts, or a combination of smolts and presmolts? If the latter, can we filter it to look at the average weight for presmolts only? And maybe smolts only for a different analysis? 
* Could we run a similar model for the spring emigration period? Figure out the dates, look at lengths of pikeminnow from the spring, convert to average weight, use average size of Chinook smolts (not presmolts) from all the Upper Salmon traps? Kevin can work on converting the spring catch into some kind of estimate of pikeminnow at Deadwater in the spring
-->

@@

@@

@@

<!-- 
After making some assumptions (e.g., on SARs) attempt to estimate how results from objective #3 could translate into impacts on adult returns (via a thought experiment or simulation approach)

Currently only using one bioenergetics model run. Could incorporate more bioenergetics models, but if so then maybe consider focusing on a single abundance estimator (e.g. Schnabel) to avoid too many combinations in the results 
-->
